Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2025-02-15 demystify.tex
updates

Sometimes students would go to great lengths just to get letters from ``top'' professors in their school (e.g., department head or dean). But as mentioned, if these professors do not know you, their letters would likely be generic and carry little value (sometimes \red{red flags}). Moreover, a top professor at your university might not be well-known to US faculty (see more details in \autoref{sec:admin-letters} and \autoref{chap:your-school}). So save the trouble and get letters from \emph{any} professors/supervisors who know you well and can write a good letter about \emph{your} research ability. It's better to have a good personalized letter about your own research ability from someone who is less well-known than a generic/weak letter from a well-known person.

@@

Your \emph{school} might not be as good as you think.  It might be T1 in your country (or in your own definition), but US faculty does not know about it, e.g., most US faculty would not know about schools in Vietnam.

Your \emph{research} might not be as strong as you think.  Doing research does not mean much (or anything) if there is no results, e.g,. publications. Publications might not have much value if they were published localled or through unknown places.  Even papers at top venues might not be as good as you think, e.g., many AI/ML/NLP faculty are not too interested in ``dataset'' papers at NeurIPS.

>>>>

Sometimes students would go to great lengths just to get letters from ``top'' professors in their school (e.g., department head or dean). But as mentioned, if these professors do not know you, their letters would likely be generic and carry little value (sometimes \red{red flags}). Moreover, a top professor at your university might not be well-known to US faculty (see more details in \autoref{sec:admin-letters} and \autoref{chap:your-school}). So save the trouble and get letters from \emph{any} professors/supervisors who know you well and can write a good letter about \emph{your} research ability (\autoref{sec:famous-lor}). It's better to have a good personalized letter about your own research ability from someone who is less well-known than a generic/weak letter from a well-known person.

@@

Your \emph{school} (\autoref{chap:your-school}) might not be as good as you think.  It might be T1 in your country (or in your own definition), but US faculty does not know about it, e.g., most US faculty would not know about schools in Vietnam.

Your \emph{research} (\autoref{chap:research-experience}) might not be as strong as you think.  Doing research does not mean much (or anything) if there is no results, e.g,. publications (\autoref{sec:publications}). Publications might not have much value if they were published localled or through unknown places.  Even papers at top venues might not be as good as you think, e.g., many AI/ML/NLP faculty are not too interested in ``dataset'' papers at NeurIPS.
